---
title: "DataScienceCapstone"
author: "Xingmin Aaron Zhang"
date: "1/23/2019"
output: html_document
---


# Section 1

## Goal:
We will explore the Swiftkey dataset to develop some intutitions about this project.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Download data

We will download the dataset directly from Coursera website. We can see that we have blogs, news and twitter texts for four languages. We will work on the English texts.
```{r}
setwd("~/git/datasciencecoursera")
fileurl = "https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip"
destfile = "Coursera-Swiftkey.zip"
if (!file.exists(destfile)) {
    download.file(fileurl, destfile = destfile)
}
# show files in the zip folder
unzip(destfile, list = TRUE)
```


```{r echo=FALSE}
## unzip file
if (!file.exists("final")){
  unzip(destfile)
}
```

# Data cleaning and exploratory analysis
We count the number of lines for three English corpus: twitter, news and blogs. From the graph we can see that blogs and news have roughly similar line counts while twitter corpus has twice line counts. 

```{r echo=FALSE, message=FALSE, fig.align='center', fig.width=4, fig.height=4}
corpusnames <- c("twitter", "news", "blogs")
EN.TWITTER.PATH = "final/en_US/en_US.twitter.txt"
EN.NEWS.PATH = "final/en_US/en_US.news.txt"
EN.BLOGS.PATH = "final/en_US/en_US.blogs.txt"

paths <- c(EN.TWITTER.PATH, EN.NEWS.PATH, EN.BLOGS.PATH)
names(paths) <- corpusnames

linecount <- function(paths) {
    counts <- vector(mode = "integer", length = length(paths))
    for (i in 1:length(paths)) {
        filecon <- file(paths[i], "r")
        counts[i] <- length(readLines(filecon, skipNul = TRUE))
        close(filecon)
    }
    counts
}
linecounts <- linecount(paths)
names(linecounts) <- corpusnames

df <- data.frame(type = corpusnames, linecount = linecounts)

library(tidyverse)
ggplot(df) + geom_bar(aes(x = type, y= linecount), stat = "identity") + ggtitle("total line counts for each type of corpuses") + theme(plot.title = element_text(hjust = 0.5)) + xlab("")
```

Before we do more sophisticated analysis, we select subsets of data from each file to reduce memory requirement. Since we have at least ~ 1 million lines for each file, we can propably get a good sense of the corpuses from 1% of the entire sample.
```{r echo=FALSE, cache=TRUE}
corpus_subset <- function(corpus_name = "twitter", percent = 0.001) {
    LINE_COUNT <- linecounts[corpus_name]
    readOrNot <- rbinom(LINE_COUNT, 1, percent)
    subset_lines <- vector(mode = "character", length = sum(readOrNot))
    i = 1
    j = 1
    filecon <- file(unname(paths[corpus_name]), "r")
    while (i <= LINE_COUNT) {
      newline = readLines(filecon, n = 1, skipNul = TRUE)
      if (readOrNot[i]){
        subset_lines[j] = newline
        j = j + 1
      }
      i = i + 1
    }
    close(filecon)
    subset_lines
}

subsetAndSave <- function() {
    en.twitter.subset <- corpus_subset("twitter", percent = 0.001)
    en.news.subset <- corpus_subset("news", percent = 0.001)
    en.blogs.subset <- corpus_subset("blogs", percent = 0.001)

    # We will save this for future use.
    if (!dir.exists("final/en_subsets")) {
         dir.create("final/en_subsets")
    }

    write(en.twitter.subset, file = "final/en_subsets/twitter_subset.txt")
    write(en.news.subset, file = "final/en_subsets/news_subset.txt")
    write(en.blogs.subset, file = "final/en_subsets/blogs_subset.txt")
}

subsetAndSave()
```

```{r echo=FALSE}
# load subsets
en.twitter.subset <- readLines(con <- file("final/en_subsets/twitter_subset.txt"))
close(con)
en.news.subset <- readLines(con <- file("final/en_subsets/news_subset.txt"))
close(con)
en.blogs.subset <- readLines(con <- file("final/en_subsets/blogs_subset.txt"))
close(con)
```


Next, we are going to count the words for each corpus. We performed some cleanings: removed unnecessary white spaces, removed numbers, converted to lower case and removed punctuations.
```{r message=FALSE, echo=FALSE}
library(tm)
#We first import the subsets into separate corpuses.
twitter_corpus<- VCorpus(VectorSource(en.twitter.subset))
news_corpus <- VCorpus(VectorSource(en.news.subset))
blog_corpus <- VCorpus(VectorSource(en.blogs.subset))

corpuses <- list(twitter_corpus, news_corpus, blog_corpus)
preprocess <- function(corpus) {
  corpus <- tm_map(corpus, removePunctuation)
  corpus <- tm_map(corpus, removeNumbers)
  #corpus <- tm_map(corpus, removeWords, stopwords(kind = "en"))
  corpus <- tm_map(corpus, stripWhitespace)
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus
}
processedCorpuses <- lapply(corpuses, preprocess)
dtms <- lapply(processedCorpuses, function(x){DocumentTermMatrix(x)})
df$docCounts <- sapply(dtms, function(x){dim(x)[1]})
df$uniqueWordCounts <- sapply(dtms, function(x){dim(x)[2]})
df$totalWordCount <- sapply(dtms, function(x){sum(x)})
```

First we looked at total words counts for each corpuses subset. From the subset of each corpuses, we can see that news have the most word count, twitter has the least even though it has most lines, and blogs are in the middle.
```{r echo=FALSE, message=FALSE, fig.align='center', fig.cap="word count for each corpus subset", fig.width=6, fig.height=3}
p1 <- ggplot(df) + geom_bar(aes(x = type, y = totalWordCount), stat = "identity") + xlab("") + ylab("count") + ggtitle("total word count") + theme(plot.title = element_text(hjust = 0.5))
p2 <- ggplot(df) + geom_bar(aes(x = type, y = uniqueWordCounts), stat = "identity") + xlab("") + ylab("count") + ggtitle("unique word count") + theme(plot.title = element_text(hjust = 0.5))

library(gridExtra)
grid.arrange(p1, p2, nrow = 1)
```


For each document/line, blogs or news have roughly similar number of words, while twitter has the least, which is totally reasonable.
```{r echo=FALSE, fig.align='center', fig.cap="word count per document for each corpus subset", fig.width=6, fig.height=3}
p3 <- ggplot(df) + geom_bar(aes(x = type, y = totalWordCount/docCounts), stat = "identity") + xlab("") + ggtitle("average word count") + theme(plot.title = element_text(hjust = 0.5))
p4 <- ggplot(df) + geom_bar(aes(x = type, y = uniqueWordCounts/docCounts), stat = "identity") + xlab("") + ggtitle("average unique word count") + theme(plot.title = element_text(hjust = 0.5))

grid.arrange(p3, p4, nrow = 1)
```

## N-gram analysis
In the next section, we are going to calculate the frequent N-gram from each corpus. 
```{r echo=FALSE}
nGramTokenizer <- function(n) { 
    function(x) {
        unlist(lapply(ngrams(words(x), n), paste, collapse = " "), use.names = FALSE)
    }   
}

oneGramTokenizer = nGramTokenizer(1)
twoGramTokenizer = nGramTokenizer(2)
threeGramTokenizer = nGramTokenizer(3)
    
```

We now start to explore n-gram distributions. We will combine the subsets of all twitters, blogs and news as one document because we only care about the combined result. 
```{r echo=FALSE}
combinedDocuments <- c(en.twitter.subset, en.news.subset, en.blogs.subset)
collapseToOne <- paste(combinedDocuments, collapse = " ")
combinedCorpus <- VCorpus(VectorSource(collapseToOne))
combinedCorpusProcessed <- preprocess(combinedCorpus)
dtm1 <- DocumentTermMatrix(combinedCorpusProcessed, list(tokenize = oneGramTokenizer, wordLengths=c(1, Inf)))
dtm2 <- DocumentTermMatrix(combinedCorpusProcessed, list(tokenize = twoGramTokenizer))
dtm3 <- DocumentTermMatrix(combinedCorpusProcessed, list(tokenize = threeGramTokenizer))

#dtm1 <- lapply(processedCorpuses, function(x){DocumentTermMatrix(x, list(tokenize = oneGramTokenizer, wordLengths=c(1, Inf)))})

#dtm2 <- lapply(processedCorpuses, function(x){DocumentTermMatrix(x, list(tokenize = twoGramTokenizer))})

#dtm3 <- lapply(processedCorpuses, function(x){DocumentTermMatrix(x, list(tokenize = threeGramTokenizer))})

```

Most frequent 15 1-grams:
```{r echo=FALSE}
mostFreqNGram <- function(x) {
    #dtmComb <- c(x[[1]], x[[2]], x[[3]])
    wordList <- colnames(x)
    freq <- colSums(as.matrix(x))

    wordFreqOneGram <- data.frame(wordList, freq)
    wordFreqOneGram %>% arrange(-freq)
}


onegram <- mostFreqNGram(dtm1)
onegram %>% head(n = 15)
```

Most frequent 2-grams:
```{r echo=FALSE}
bigram <- mostFreqNGram(dtm2) 
bigram %>% head(n = 15)
```

Most frequent 3-grams:
```{r echo=FALSE}
trigram <- mostFreqNGram(dtm3) 
trigram %>% head(n = 15)
```

## Conclusions

From our exploratory analysis, we can conclude that:

* There are more twitter lines than news or blogs
* News have more total words and total unique words, followed by blogs and twitter.
* Blogs have the most total words and unique words per document, closely followed by news. While twitters have the lease total words and unique words per document.
* We also showed the most frequent words, word pairs, and word triplets. 

Going forward, we can use the N-gram frequency to make predictions on the next input.


# Section 2

## Goals
Build a n-gram model to predict the next word

## Prediction with data frame implementation
The idea of the predictive model is using bigram to predict word based on previous 1-word, and using trigram to predict next word based on previous bi-gram.

One straightward way to implement the idea is using a data frame to save all 1,2 and 3-grams. In this dataframe, there will be three columns for individual words. The first column is just 1-grams words. The second column is the second word of bigrams, so that concatenating it with the word in the first column gives a bigram. This rule extends to the third column and trigrams. 

```{r}
onegram_dataframe <- onegram %>% rename(word1 = wordList) %>% mutate(word1 = as.character(word1))
bigram_dataframe <- bigram %>% separate(wordList, c("word1", "word2"), " ")
trigram_dataframe <- trigram %>% separate(wordList, c("word1", "word2", "word3"), " ")

resource <- onegram_dataframe %>% inner_join(bigram_dataframe, by = "word1") %>% inner_join(trigram_dataframe, by = c("word1", "word2"))
```

```{r}
predictWord1 <- function() {
    onegram_dataframe[1,1]
}

predictWord2 <- function(query) {
    selection <- resource %>% filter(word1 == query)
    candidates <- unique(selection$word2)
    if (length(candidates) > 0) {
        return(candidates[1])
    } else {
        return(predictWord1())
    }
}

predictWord3 <- function(query1, query2) {
    selection <- resource %>% filter(word1 == query1 & word2 == query2)
    candidates <- unique(selection$word3)
    if (length(candidates) > 0) {
        return (candidates[1])
    } else {
        return(predictWord2(query1))
    }
}

processSentence <- function(sentence) {
    sentence <- removePunctuation(sentence)
    sentence <- removeNumbers(sentence)
    sentence <- stripWhitespace(sentence)
    sentence <- tolower(sentence)
    sentence
}

predictNext <- function(sentence, n = 3) {
    processed <- processSentence(sentence)
    tokens <- strsplit(sentence, " ")[[1]]
    NUM_TOKENS <- length(tokens)
    if (NUM_TOKENS <= 1) {
        predictWord2(tokens[1])
    } else {
        predictWord3(tokens[NUM_TOKENS - 1], tokens[NUM_TOKENS])
    }
}

# trim end word
trimEndWord <- function(x) {
  splitted <- strsplit(x, " ")
  sapply(splitted, function(x) {paste(x[1 : length(x) - 1], collapse = " ")})
}

# combined training method
train <- function(percent = 0.01, n = 4) {
    # subsetting data
    corpus_sampling <- c(corpus_subset("twitter", percent), 
                         corpus_subset("blogs", percent), 
                         corpus_subset("news", percent))
    # combining data
    corpus_sampling <- str_c(corpus_sampling, collapse = " ")
    corpus_sampling <- VCorpus(VectorSource(corpus_sampling))
    # preprocess data
    preprocessed <- preprocess(corpus_sampling)
    # create unigram, bigram, ... n-gram
    require(hash)
    require(triebeard)
    wordhash <- hash()
    wordtrie <- trie(character(), numeric())
    for (i in 1:n) {
        tokenizer = nGramTokenizer(i)
        dtm <- DocumentTermMatrix(preprocessed, list(tokenize = tokenizer, wordLengths=c(1, Inf)))
        newWordList <- colnames(dtm)
        newWordCount <- dtm$v
        if (i == 1) {
            total <- sum(newWordCount)
            trie_add(wordtrie, keys = newWordList, values = newWordCount/total)
        } else {
            newWordParent <- trimEndWord(newWordList)
            parentCount <- values(wordhash[newWordParent])
            trie_add(wordtrie, keys = newWordList, values = newWordCount/parentCount)
        }
        clear(wordhash) # just save keys that are required for next round
        .set(wordhash, keys = newWordList, values = newWordCount)
    }
    rm(wordhash)

    wordtrie
}

wordhash <- train(percent = 0.0001)

wordtrie <- trie(character(), numeric())
keys(wordhash)

trie_prob <- function(trie, n) {
  
  for (i in n:1) {
    keys <- get_keys(trie)
    keys_current <- keys[sapply(strsplit(keys, " "), length) == i]
    values_current <- unlist(prefix_match(trie, keys_current))
    keys_trim <- trimEndWord(keys_current)
    values_trim <- unlist(prefix_match(trie, keys_trim))
    if (i >= 2) {
      trie_add(trie, keys_current, values_current/values_trim)
    } else {
      trie_add(trie, keys_current, values_current/sum(values_current))
    }
  }
  trie
}

wordtrie <- trie(keys = c("A", "A a", "A b", "A c", "A a a", "B", "B a", "B b", "B c"), values <- c(5, 3, 1, 1, 1, 6, 2, 2, 2))
trie_prob(wordtrie, 3)
predictNext <- function(sentence) {
    
}
```

```{r}
quizes <- c("The guy in front of me just bought a pound of bacon, a bouquet, and a case of", 
               "You're the reason why I smile everyday. Can you follow me please? It would mean the", 
               "Hey sunshine, can you follow me and make me the",
               "Very early observations on the Bills game: Offense still struggling but the", 
               "Go on a romantic date at the", 
               "Well I'm pretty sure my granny has some old bagpipes in her garage I'll dust them off and be on my", 
               "Ohhhhh #PointBreak is on tomorrow. Love that film and haven't seen it in quite some", 
               "After the ice bucket challenge Louis will push his long wet hair out of his eyes with his little", 
               "Be grateful for the good times and keep the faith during the", 
               "If this isn't the cutest thing you've ever seen, then you must be")
for (i in 1: length(quizes)) {
    print(paste(i, predictNext(quizes[i])))
}
```

