---
title: "Car Transmission on Fuel Efficiency"
author: Xingmin Aaron Zhang
output: pdf_document
---

Our goal for this report is to explore the effect of car transmission, manual or automatic, on fuel efficiency measurement by miles per gallon. We used the mtcars dataset in R for this project.

## Load Data and Exploratory analysis

The dataset has 11 variables and 32 observations. By default, all variables are considered numeric. We corrected some into factors, including cyl, vs, am, gear and carb. When we plot fuel efficiency by the type of transmission (Figure 1 Left), we found that the mpg appears higher for manual transmissions. Therefore, one may hypothesize that cars with manual transmission have higher fuel efficiency.

```{r message=FALSE, echo=FALSE}
attach(mtcars)
mtcars$cyl = as.factor(mtcars$cyl)
mtcars$vs = as.factor(mtcars$vs)
mtcars$am = as.factor(mtcars$am)
mtcars$gear = as.factor(mtcars$gear)
mtcars$carb = as.factor(mtcars$carb)
```


```{r message=FALSE, fig.align='center', fig.width=2,fig.height=2, echo = FALSE}
library(ggplot2)
p1 <- ggplot(mtcars) + geom_violin(aes(x = factor(am), y = mpg, fill = factor(am)), draw_quantiles = c(0.5)) + 
    scale_fill_discrete(breaks = c(0, 1), labels = c("automatic", "manual")) + 
    xlab("") + scale_x_discrete(breaks = c(0, 1), labels = c("automatic", "manual")) + 
    theme(legend.position = "none")
```

Before we used the variables for building models, we looked at their correlations (Supplement Figure 1). We could identify several variables that have high correlation. Therefore, we decided to use variable inflication factors (VIF) to remove highly correlated variables. 
```{r fig.align='center', fig.width=6, fig.height=6, fig.cap="correlation matrix", include=FALSE}
# plot inspired by http://www.sthda.com/english/wiki/scatter-plot-matrices-r-base-graphs
panel.cor <- function(x, y){
    usr <- par("usr"); on.exit(par(usr))
    par(usr = c(0, 1, 0, 1))
    r <- round(cor(as.numeric(x), as.numeric(y)), digits=2)
    txt <- paste0("R = ", r)
    cex.cor <- 0.8/strwidth(txt)
    text(0.5, 0.5, txt, cex = cex.cor * r)
}

upper.panel<-function(x, y){
  points(x,y, pch = 19, cex = 0.5)
}
pairs(mtcars[,-1], gap = 0.5, lower.panel = panel.cor, upper.panel = upper.panel,
      main ="mtcars: regressor correlation")
```

## Statistical Analysis
Our first model is simply a linear relationship between mpg and all variables. As expected, disp, hp and wt have high VIF due to their correlation. Therefore, we remove them one by one and found that after removing both hp and disp, the VIFs look better (Supplement).  

```{r message=FALSE}
fit <- lm(mpg ~ ., data = mtcars)
library(car)
sqrt(vif(fit))
```



```{r echo=FALSE, include=FALSE}
variables <- colnames(mtcars)
fit2 <- lm(mpg ~ ., data = mtcars[,variables != "hp"])
fit3 <- lm(mpg ~ ., data = mtcars[,variables != "hp" & variables != "disp"])
sqrt(vif(fit3))
```

In the next step, we built nested models with the remaining variables and checked whether adding each variables improved prediction. We found that only am, cyl and wt did. Add interactions among them did not improve residue reduction, so we chose to build the model with am, cyl and wt without interaction terms. 

```{r echo=FALSE}
mtcars_subset <- mtcars[,variables != "hp" & variables != "disp"]
model1 <- lm(mpg ~ am, data = mtcars_subset)
model2 <- update(model1, mpg ~ am + cyl)
model3 <- update(model2, mpg ~ am + cyl + drat)
model4 <- update(model3, mpg ~ am + cyl + drat + wt)
model5 <- update(model4, mpg ~ am + cyl + drat + wt + qsec)
model6 <- update(model5, mpg ~ am + cyl + drat + wt + qsec + vs)
model7 <- update(model6, mpg ~ am + cyl + drat + wt + qsec + vs + gear)
model8 <- update(model7, mpg ~ am + cyl + drat + wt + qsec + vs + gear + carb)
anova(model1, model2, model3, model4, model5, model6, model7, model8)
```

Final linear model is shown below. The residues from this model spreaded randomly, suggesting that the model is working fine (Figure 1 Right).
```{r}
model <- lm(mpg ~ am + cyl + wt, data = mtcars_subset)
```

```{r echo=FALSE, include=FALSE}
model_int <- update(model, mpg ~ am * cyl * wt )
anova(model, model_int)
```

```{r echo=FALSE, fig.align='center', fig.height=2, fig.width=8, fig.cap="Left: fuel efficiency changes with transmission types; Right: residues of final linear model", message=FALSE}
d <- data.frame(residues = resid(model), fitted = fitted.values(model))
p2 <- ggplot(d, aes(x = fitted, y = residues)) + geom_point() + geom_hline(yintercept = 0, color = "red")
require(gridExtra)
grid.arrange(p1, p2, ncol = 2, widths = c(2, 6))
```

The transmission type variable, am, has a coefficient of 0.15, but its variance is so large that it did not pass the t test (p value = 0.91). Rather, increasing the number of cylinders or weight, significantly reduce fuel efficiency. Therefore, we can conclude with high confidence (99%) that the type of transmission did not significantly affect fuel efficiency. 

```{r}
summary(model)$coefficients
```

## Conclusion
We conclude that fuel efficiency is not significantly impacted by the type of transmissions based on the mtcars dataset.
